---
title: "NC Bike Crashes"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Getting started

## Clone assignment repo

1. Go to your repo `appex03-[github_name]` on GitHub.

2. Click on the green **Clone or download** button, select **Use HTTPS** 
   (this might already be selected by default, and if it is, you'll see the 
   text **Clone with HTTPS** as in the image below). 
   Click on the clipboard icon to copy the repo URL.

3. Go to RStudio Cloud and into the STA 199 course workspace. 
   Create a **New Project from Git Repo**. You will need to click on the down 
   arrow next to the **New Project** button to see this option.

4. Copy and paste the URL of your assignment repo (done in step 2) into 
   the dialog box.

5. Click OK, and you should see the contents from your GitHub repo in the 
   `Files` pane in RStudio. 

## Configure git

Type (copy) the following lines of code in the **Console** in RStudio - 
filling in your name and email address.

```{r config-git-ex, eval=FALSE}
library(usethis)
use_git_config(user.name="your name", user.email="your email")
```

# Packages and Data

```{r load-packages}
library(tidyverse)
```

```{r}
ncbikecrash <- read_csv2("data/nc_bike_crash.csv")
```

# Tasks

## Task 1

Identify the most common driver speed limit for when bike crashes occur.

```{r task-1}

```

## Task 2

Filter `ncbikecrash` for crashes in residential areas where the driver age
group is 0-19.

```{r task-2}

```

## Task 3

What is the mean hour for when a crash occurs in Durham County for each month?

```{r task-3}

```

## Task 4

Plot your result from Task 3.

```{r task-4}

```

# Submission

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.

# Slide notes

```{r}

```

# References

1. Bicycle Crashes. (2020). Chapelhillopendata.org. Retrieved 21 January 2020, from https://www.chapelhillopendata.org/explore/dataset/bicycle-crash-data-chapel-hill-region/information/?disjunctive.city&disjunctive.county&disjunctive.crashday&disjunctive.crashsevr&disjunctive.crashyear
