---
title: "NC Bike Crashes"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Getting started

1. Clone your repo `appex03-[github_name]` on GitHub to create a new project
   in RStudio Cloud under the STA 199 class space.

2. Configure git
      ```{r config-git-ex, eval=FALSE}
      library(usethis)
      use_git_config(user.name="your name", user.email="your email")
      ```

# Packages and Data

Let's load package `tidyverse`.

```{r load-packages}
library(tidyverse)
```

To load the data we will use function `read_csv2()` and save the data frame
as an object named `ncbikecrash`.

```{r}
ncbikecrash <- read_csv2("data/nc_bike_crash.csv")
```

# Tasks

## Task 1

Identify the most common driver speed limit for when bike crashes occur.

```{r task-1}

```

## Task 2

Filter `ncbikecrash` for crashes in residential areas where the driver age
group is 0-19.

```{r task-2}

```

## Task 3

What is the mean hour for when a crash occurs in Durham County for each month?

```{r task-3}

```

## Task 4

Plot your result from Task 3.

```{r task-4}

```

# Submission

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.

# Slide notes

```{r}

```

# References

1. Bicycle Crashes. (2020). Chapelhillopendata.org. Retrieved 21 January 2020, from https://www.chapelhillopendata.org/explore/dataset/bicycle-crash-data-chapel-hill-region/information/?disjunctive.city&disjunctive.county&disjunctive.crashday&disjunctive.crashsevr&disjunctive.crashyear
